# Kira Plastinina Unsupervised Modelling

## 1. Problem Definition

### a. Defining the problem

Kira Plastinina is a Russian brand that is sold through a defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, Philippines, and Armenia. The brand’s Sales and Marketing team would like to understand their customer’s behavior from data that they have collected over the past year. More specifically, they would like to learn the characteristics of customer groups.

### b. Understanding the Context

Kira Plastinina, is the daughter of Russian millionaire Sergei Plastinina, who, in 2008, launched a namesake fast fashion line, opened 12 stores in the U.S. She is the world’s youngest fashion designer who opened her first boutique when she was just 14. Kira Plastinina is a Russian brand that is sold through a defunct chain of retail stores in Russia, Ukraine, Kazakhstan, Belarus, China, Philippines, and Armenia.

### c. Experimental Design

1.Problem Definition
2.Data Sourcing
3.Check the Data
4.Perform Data Cleaning
5.Perform Exploratory Data Analysis  (Univariate, Bivariate & Multivariate)
6.Implement the Solution
7.Challenge the Solution
8.Follow up Questions

### d. Data relevance


## 2. Data Sourcing
```
# Installing necessary libraries
install.packages('tidyverse')
library(tidyverse)
library(magrittr)
library(grid)
library(devtools)
```
```{r}
# Loading the data
shopper <- read.csv("http://bit.ly/EcommerceCustomersDataset", sep = ",", quote = "/")
head(shopper)
```

## 3. Checking the data
```{r}
# checking the number of columns and rows

dim(shopper)
```
We can see we have 12330 rows and 18 columns

```{r}
# Checking or the type of data that we have
str(shopper)
```

We have both numerical and categorical data

## 4. Data Cleaning
```{r}
# Checking or missing values

colSums(is.na(shopper))
```
There are some null values
```{r}

# removing the missing values

shopper <- na.omit(shopper)
colSums(is.na(shopper))
```
The data is now free from missing values
```{r}
# Checking for duplicates

anyDuplicated(shopper)
```
There are some duplicates which are 159 in total
```{r}
# Dropping duplicates
shopper = distinct(shopper)

# Ckecking whether the duplicates have been successfully dropped
anyDuplicated(shopper)
```

## 5. Exploratory Data Analysis

### 5.1 Univariate Analysis
```{r}
# Checking the summary for the variables
summary(shopper)
```
we can see that most variables have a lot of imbalance

#### 5.12 Boxplots & Histograms

```{r}

# previewing the numerical variables' histograms and boxplots
par(mfrow=c(2,2))
for(i in 1:10) {
  hist(shopper[, i], main=names(shopper)[i], xlab = NULL)
  boxplot(shopper[,i], main=names(shopper)[i], horizontal = TRUE)}
```
we can see that all the variables have outliers and are not normally ditributed

#### 5.13 Bar Graphs

```{r}
# create tables of all categorical variables to be able to create bar plots with them
mnth <- table(shopper$Month)
os <- table(shopper$OperatingSystems)
bwr <- table(shopper$Browser)
reg <- table(shopper$Region)
traf <- table(shopper$TrafficType)
visitor <- table(shopper$VisitorType)
wknd <- table(shopper$Weekend)
rev <- table(shopper$Revenue)
```

```{r}
# month
par(mfrow=c(1,1))
barplot(mnth)
```

The most popular month is May and the least popular is Feb. This may be because the countries invloved are starting the summer season and their outfits are for the season. November is also quite popular and the assumption is that people are shopping for the holidays.During this season there are many offers

```{r}
# operating system
par(mfrow=c(1,1))
barplot(os)
```

The second Operating system is preffered to the others
```{r}
# browser
par(mfrow=c(1,1))
barplot(bwr)
```
Browser number 2 is commonly used by the customers. My money is on "Chrome"

```{r}
# region
par(mfrow=c(1,1))
barplot(reg)

```

Region No. 1 seems to be quite popular
```{r}
# traffic type
par(mfrow=c(1,1))
barplot(traf)
```
```{r}
# visitor type
par(mfrow=c(1,1))
barplot(visitor)
```
The site seems to have more regular customers than new visitors. They have done a good job retaining their regulars, however they may need to advertise more so as to get customers.

```{r}
# revenue
par(mfrow=c(1,1))
barplot(rev)
```
The revenue column is not fairly balanced

### 5.2 Bivariate Analysis

```{r}
#using a heat map to visualize variable correlations
library(ggcorrplot)
shopper_num <- shopper[,1:10]
corr_df <- cor(shopper_num)
ggcorrplot(round(corr_df, 2) ,lab = T,type = 'lower')

```
As I suspected, BounceRates is very highly correlated to ExitRates, Administrative is correlated with Administrative_Duration, Informational is highly correlated to Informational_Duration, and ProductRelated is highly correlated with ProductRated_Duration.Therefore, we will have to drop one variable of each of the highly correlated pairs to reduce dimensionality and redundancy.

```{r}
# plotting the distribution of Revenue per Month
par(mfrow=c(1,1))
rev_mnth <- table(shopper$Revenue, shopper$Month)
barplot(rev_mnth, main = "Revenue per Month", col = c("pink", "cyan"), beside = TRUE, 
        legend = rownames(rev_mnth), xlab = "Month")
```
The False is much more than the true

```{r}
# plotting the distribution of Revenue per Visitor Type
par(mfrow=c(1,1))
rev_visitor <- table(shopper$Revenue, shopper$VisitorType)
barplot(rev_visitor, main = "Revenue per Visitor Type", col = c("pink", "cyan"), beside = TRUE, 
        legend = rownames(rev_visitor), xlab = "Visitor Type")
```
The False is much more than the true


## 6. Implementing the solution


```{r}
# selecting the predictor and target variables

sup_shopper <- shopper[, c(1,3,5,7,9,10,11,12,13,14,15,16,17)]
sup_shopper.class <- shopper[, 18]

# Preveiwing the predictor variables
head(sup_shopper)

# Previewing the target variables
head(sup_shopper.class)

```

```{r}
# convert the factors into numerics
sup_shopper$Month <- as.numeric(sup_shopper$Month)
sup_shopper$OperatingSystems <- as.numeric(sup_shopper$OperatingSystems)
sup_shopper$Browser <- as.numeric(sup_shopper$Browser)
sup_shopper$Region <- as.numeric(sup_shopper$Region)
sup_shopper$TrafficType <- as.numeric(sup_shopper$TrafficType)
sup_shopper$VisitorType <- as.numeric(sup_shopper$VisitorType)
sup_shopper$Weekend <- as.numeric(sup_shopper$Weekend)

# Checking to see if datatype has changed
str(sup_shopper)
```
```{r}
# Scaling the data using MinMax scaler
normal <- function(x) (
  return( ((x - min(x)) /(max(x)-min(x))) )
)
Shopper_new <- as.data.frame(lapply(sup_shopper, normal))
summary(Shopper_new)
```
### 6.1 K Means
```{r}
# applying k-means with k = 3
k_result <- kmeans(Shopper_new, 3)
```

```{r}
# previewing the number of records in each cluster
k_result$size
```
```{r}
k_result$centers
```

```{r}
# visualizing the clusters
par(mfrow = c(1,2), mar = c(5,4,2,2))
```


```{r}

# plotting Administrative vs Informational
plot(Shopper_new[,1:2], col = sup_shopper.class)
```

```{r}
# plotting Special Day vs Month
plot(Shopper_new[,6:7], col = k_result$cluster)
```

```{r}

# showing how the clusters respond to the classes
table(k_result$cluster, sup_shopper.class)
```

options(repr.plot.width = 11, repr.plot.height = 6)
fviz_cluster(kmeans_res, df)

### 6.2 Heirachial Clustering
```{r}
# first we compute the euclidean distance
df <- dist(Shopper_new, method = "euclidean")
```

```{r}
# then we compute hierarchical clustering using the Ward method
hier <- hclust(df, method = "ward.D2" )
```

```{r}
# finally, we plot the dendogram
plot(hier, cex = 0.6, hang = -1)
```



## 7. Conclusion
The clusters of kmeans are more defined when comparing them to the clusters hierachical clusters. Therefore, kmeans should be given preferance when clustering customer groups
